% \cleardoublepage

\abstract

With Unmanned Aerial Vehicles (UAVs) becoming more and more popular, the need to have agile, resilient, cost-effective and highly available unmanned aerial systems becomes eminent. Cloud computing especially AWS, which is the cloud provider of choice in this thesis, presents a great advantage at being able to provide an environment where Unmanned Aerial Systems with the aforementioned characteristics can be built. Unmanned Aerial Mobility is a sector that is growing so much that the need to have robust systems becomes also necessary to have. Therefore, this thesis aims at assessing how feasible it is to run applications or unmanned aerial system applications on the cloud.

The thesis goes on to elaborate on various techniques used to deploy the AWS infrastructure of the proposed solution, like Infrastructure as Code and serverless design approach, for a more robust, resilient, highly available and agile infrastructure. The proposed solution is designed for a full unmanned aerial system including actual hardware components, but along the way, focus switched to rather simulating parts of the solution like the UAV to prove the concept due to different challenges faced with acquiring various hardware parts that were needed along with the cost attached to them. Progress that was already made on the hardware implementation is presented and discussed though.

The approach taken to develop the proposed solution, despite multiple challenges faced that opened rooms for improvements, has proven that it is possible to run unmanned aerial system applications on the cloud and that it is a viable solution that can be applied in the unmanned aerial mobility sector.

\keywords AWS, UAV, UAS, Serverless