%%%---------------------------------------------------------------%%%
%%% Wyzsza Szkola Gospodarki Bachelor's Thesis                    %%%
%%% Prepared by Bruno Axel Kamere                                 %%%
%%% Inspired by Artur M. Brodzki & Piotr Woźniak's WUT template.  %%%
%%% Computer Engineering and Mechatronics Department              %%%
%%% Wyzsza Szkola Gospodarki w Bydgoszczy, 2022                   %%%
%%%---------------------------------------------------------------%%%
% -------------------------------------------------------------------
% 10. ACKNOWLEDGEMENTS                                              %
% -------------------------------------------------------------------

\cleardoublepage

%/-------------------------------- SECTION START --------------------------------/%

\section*{\centering \Large Acknowledgements}

\begin{acknowledgements}

    Looking back at my journey that led to this point, I would like to take some time and thank everyone that has helped me throughout my studies, and design, development, and testing of this final engineering work. The moral support received throughout this period is unprecedented.

    I would like to first and foremost thank my lovely parents. They have been there for me in each single step that led to where I am and what I have achieved today. They have encouraged me, believed in me, and supported me in various ways. Thank you.

    Next, I would like to also thank a lot my thesis supervisor, Ocetkiewicz Tomasz, mgr inż.; first, for believing in my ability to conduct my research towards the execution of my project and second, for the unprecedented advice and support I have received throughout my studies and throughout my final engineering research and project execution. Thank you.

    I want to also take a moment to thank the WSG university’s institute of informatics and mechatronics professors and staff for the knowledge and skills they have provided me throughout my studies. They have inspired me to like more my field of studies, due to the challenges provided to me along the way. Thank you.

    Finally, I would not finish without thanking my classmates, colleagues and friends who have been part of my support system and have given me ideas and support throughout my studies, until this day. A big thanks to you.


\end{acknowledgements}

%/--------------------------------- SECTION END ---------------------------------/%
